Global adjoint tomography -- Model GLAD-M25

### 2018-10-19 main.tex
fix space in figure
Updates from ShareLaTeX

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
  \caption{Source corrections for 1,040 out of 1,480 events used in the structural inversion. (a) Map view of depth changes. (b) Distribution of seismographic stations used for source inversions. (c) Depth change relative to the original global CMT Catalog depth. (d)--(f) Histograms of depth, origin time, and scalar moment changes relative to the CMT Catalog.
  {\color{red} Wenjie: please put a space between ``depth'' and ``km'' in the x-axis labels of figures C and D.}
  }
  \label{fig:source_correction}
\end{figure}

@@

The inversion went through ten iterations in a number of stages, as documented in this section.
The behavior of the overall misfit function~(\ref{eq:misfit}) as well as its behavior in the various measurement categories is shown in Fig.~\ref{fig:misfit}.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/misfit.pdf}
  \caption{Evolution of phase misfits from GLAD-M15 to GLAD-M25.
  Each color denotes the different stages of inversions, between
  which we make changes to the inversion by either tuning the
  weighting strategies or adding more data.
  (a) Evolution of the total phase misfit. (b) - (j) Misfit in
  each period band and component. (e) - (g) From GLAD-M18,
  we future split the 40-100 sec period band into two
  measurement categories: body(red diamond) waves and surface waves
  (red square).
  {\color{red} Wenjie, why do the graphs overlap at iteration 22, but not at iteration 18?Shouldn't 22 look like 18, i.e., no overlapping points?}
  }
  \label{fig:misfit}
\end{figure}

@@

The misfit reduction for 17--40~s body waves (Figs.~\ref{fig:misfit}b--d) tapers off by iteration 21, prompting us to add more earthquakes and change the weighting strategy again.

@@

At iteration~22 we added another 440 earthquakes to the database,
bringing the total to 1,480 event,
and we changed the 40--100~s surface wave weights back to their setting during Stage~I.
During this stage we also switched from a nonlinear conjugate gradient optimization algorithm to an L-BFGS quasi-Newton method.

\subsection{Misfit assessment}

In the previous section we discussed the evolution of the misfit through the three key stages of the inversion.
It is important to note that ``the misfit function'' is, in fact, a continually moving target, because at every iteration the number of measurements increases as the model improves,
and the number of earthquakes increases at iterations~18 and~22.
In this section we calculate specific changes in misfit using all 1,480 earthquakes and an identical set of weightings and windows for three models, namely, GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
Table~\ref{table:misfit_reduction_M15_M25} summarizes the changes in fit in the twelve measurement categories
between the new model, GLAD-M25, and its starting model, GLAD-M15, and between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.
In all categories we observe significant misfit reductions,
with dispersive 40--100~s surface waves exhibiting the largest misfit reduction.
The improvements in fit per component are comparable in all period bands,
indicating that the various categories are reasonably well balanced in the assessment of misfit.

@@

\subsection{Histogram comparisons}

Another way to evaluate model performance is by assessing the distribution
of measurements in the various categories.
Again we use all 1,480 events and a set of identical windows on all three components
to assess GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
The total number of selected windows exceeds 18~million.
Fig~\ref{fig:phase_hist} shows histograms of the resulting phase
measurements in all twelve measurement categories.
We observed that the distributions generally become better centered on zero,
and that the standard deviations are steadily reduced.
Again we note that the inversion is aimned at reducing the overall misfit,
so there are small tradeoffs between different measurement categories.

Fig~\ref{fig:amp_hist} shows histograms of the amplitude
measurements for all twelve measurement categories,
which are not used in the current inversion.
Despite this,
we observe modest reductions in the standard deviations of the histograms.
The histograms are nicely centered, indicating that the moment magnitudes are suitably selected.
In the next phase of our ongoing inversion we plan to begin assimilating these amplitude measurements,
while simultaneously adding shear attenuation as a new model parameter.

@@

\section{Model Evaluation}

Here, we present two ways that used to evaluate the quality of our model:
resolution analysis and held-out data test.

\subsection{Resolution Analysis}
Checkboard test was commonly used a resolution test method but it is at the
same cost of inversion of GLAD-M25, which will cost millions of CPU hours.
Due to the very demanding computational requirements, we used the 'point
spread function to assess the imaging quality in models GLAD-M25.

\subsection{Held-out Dataset Test}
Following the approach by \cite{tape2009adjoint}, \cite{bozdaug2016global},
unseen events are used to check the performance of our
model. We revisited the Global CMT catalogue,
picked all the events whose magnitude is between 6.3 and 7.0, which hasn't
been used in our inversion. The reason why we set the lower bound to 6.3
instead of 5.5, is those earthquakes have good enough data and generates
more measurements at the global scale.
We calibrated the scalar moment and origin time in the GLAD-M25, and there
are 360 events left that has enough windows. Fig.\ref{fig:events_360} shows
the distribution of 360 earthquake that we used as held-out dataset

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/events_360.pdf}
  \caption{Locations of 360 held-out earthquakes used to assess the traveltime misfit in the model assessment stage. Theses events are not used in the structural inversion. (a) Beach balls of earthquakes. Same color conventions as used in the \ref{fig:event_1480} (b) and (c) Histograms of moment magnitude and depth.}
  \label{fig:events_360}
\end{figure}

First, we evaluate the model performance by misfit reduction. Same windows and
weightings are used across models. Table.\ref{table:misfit_reduction_M00_M25_360}
shows the misfit reduction from M15 to M25 and Table.\ref{table:misfit_reduction_M00_M25_360}
is from M00 to M25. It again shows misfit reduction in all categories in
our held-out dataset, similar to what we observed from the inversion dataset.
The reduction are slightly smaller, partly due to the reason that we didn't
do waveform-type inversion as we mentioned in the source inversion stage but
only did a grid search to calibrate the scalar moment and origin time.

@@

Second, we also plotted the histograms of phase measurements in Fig.\ref{fig:phase_hist_360}. We also observed clear variance reduction in all the 12 categories from GLAD--M00 to GLAD--M25.

To summarize, both the misfit reduction and histogram improvements indicates that our model performs good with data that hasn't been used in our inversion. We expect to see similar behavior for the future earthquakes.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
  \caption{Histogram of phase measurements similar to \ref{fig:phase_hist} except for 360 held-out earthquakes.}
  \label{fig:phase_hist_360}
\end{figure}

\section{Models}

\subsection{Global Velocity Structure}

{\color{Red} Wenjie: Plan to work more on this part. But do you any suggestion what things should I talk about?}

In Fig.\ref{fig:global-vs}, the global map of isotropic $V_s$ is plotted at certain depths.
As comparisons, we also plotted two other models, S362ANI+M{\citep{moulik2014anisotropic},
which is the updated version of our starting model but with mode data added
into the inversion, and S40RTS\citep{ritsema2011s40rts}. At the first glance,
you may notice that all the models agree at the long wavelength structures.
At 2800km depth, our model is very close to S362ANI+M, with more extended
features at the LLSVP.

The value ranges are labeled on the top left on each figure. It is obvious the
value ranges in our model is generally larger than other two models, which is
consistent with \cite{french2014whole}.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
  \caption{Map views of global $V_s$ perturbations at various depths for out model
  GLAD-M25(left column), S362ANI+M(middle column)\citep{moulik2014anisotropic}
  and S40RTS(right column)\citep{ritsema2011s40rts}. The perturbations are
  calculated based on each model's own 1D profile. The values(upper-left corner
  of each figure) denotes the minimum/maximum perturbations for each model at
  the corresponding depth. The green circles denotes the locations of
  hotspots\citep{montelli2006catalogue}. The range of the colorbar is the same
  for each row and the range value is labeled on the most left, right after
  the depth.}
  \label{fig:global-vs}
\end{figure}

%\begin{figure}
%\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
%  \caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI+M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}. For LLNL-G3Dv3, the depths is labeled on the right bottom based on its own mesh spacing. Other plotting conventions are used similar as in Figure \ref{fig:global-vs}.}
%\label{fig:global-vp}
%\centering
%\end{figure

The other prominent feature of our models is that we can also constrain $V_p$ as an
independent model parameters. Fig.\ref{fig:global-vp} shows our isotropic $V_p$
structures at several depths. As comparisons, we also showed two more global
$V_p$ models, LLNL-G3Dv3\citep{simmons2012llnl}} and GAP-P4\citep{fukao2013subducted}.

At 100km depth, our model shows prominent ocean ridges at the realm of pacific
oceans, which are relatively slow velocity regions, compared to other two vp models.
On the other hand, the continent slabs, such as Australia, South Africa,
North America and Europe, is more prominent in our model.

For upper mantle, the LLNL-G3Dv3 shows the largest variations. For example,
the 500km, the LLNL model shows very strong slow velocity anomalies at
Hawaii and other pacific hotspots, such as Samoa and Tahiti.
For middle mantle at about 1000km, all them models all shows a few major
subduction zones, such as the South America, Fiji and Sumatra regions.
At lower mantle, such as 2000km and 2800km, LLNL-G3Dv3 and GAP-P4 tends to
fade out, even though the patterns are very similar among them, such as
the LLSVP regions.

** Note: add spherical harmonic analysis later **

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
  \caption{Map views of global $V_p$ variations at various depths for our model
  GLAD-M25(left column), LLNL-G3Dv3(middle column) \citep{simmons2012llnl} and
  GAP-P4(\citep{fukao2013subducted}).
  For LLNL-G3Dv3, the depths is labeled on the right
  bottom based on its own mesh spacing. Other plotting conventions are used
  similar as in Figure \ref{fig:global-vs}.}
\label{fig:global-vp}
\centering
\end{figure}

For the following sections, we will discuss the velocity structures in regional
areas.

@@

{\color{Red} Wenjie: Ready for Jeroen to edit}

The deployment of USArray has dramatically increased the data overage on the
continental United States. In this section, we compare our GLAD-M25 with
together with two global models, S362ANI+M, S40RTS, and two regional models,
US22\citep{zhu2017radial}, SL2013NA\citep{schaeffer2014imaging}.

US22 is radially anisotropic model build based on adjoint tomography using
USArray data from 180 regional earthquakes using 15-50sec short-period
body waves and 25-150sec long-period surface waves.
SL2013NA is an upper-mantle global shear wave speed model using multimode
surface waveform tomography and primarily focused on the north American
region.

The North American region is featured by a large, high-velocity cratonic
lithosphere, bounded by the Rocky Mountain Front to the west and continental
margin to the east. For both sides the lithosphere has been deformed by
low velocity structures thus form a sharp boundary.

At 100km, our model shows a much sharpened boundary between the carton
and surrounding low velocity structures, especially compared with
two global models, S362ANI+M and S40RTS, yet stay very similar to
two regional models, US22 and SL2014NA. At such depth,
we are observed a very strong expression of the Snake River Plain(
with Yellowstone) and Raton hotspot, with their depth extending to 200km.
The very high-velocity craton extend to 200km, with its very core part to
300 km, similar to US22 while SL2013NA shows it almost disappeared at such depth.
Again, the Wyoming craton and Medicine Hat Block shows a very strong lithosphere
root from the very shallow depth to 400km, which is also similar to US22 but
hard to observe in SL2013NA. Similar case is the craton at Yavapai and
Mazatzal Blocks, which define the southern bound of the large craton.

@@

At the North, our models shows a extended high velocity craton beneath the 
Greenland, though clearly separated with the North America Craton,
bounded at the relatively low velocity structure at Barffin Bay and Labrador
Sea, with North American Craton followed nicely with the coastline. In the
north west region, our models shows the most clear picture of
Aleutian subduction zones, with it high velocity feature down to 400km.
In the northeastern part, the Iceland hotspot has been greatly enhanced,
especially at 300km and 400km compared to S362ANI+M.

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
  \caption{Map views of $V_s$ variations of North America at various depths
  for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS)
  and regional(US22\citep{zhu2017radial} and SL2013NA\citep{schaeffer2014imaging})
  models. Green circles denotes the locations of hotspots. For SL2013NA, we
  showed the 610km instead of 600km due to its own mesh.}
\label{fig:america-vs}

@@

Fig.\ref{fig:europe-vs} shows the isotropic $V_s$ structures at Europe. As
comparisons, we also showed S362ANI+M, S40RTS and one regional model EU60
\citep{zhu2015seismic}. Compared to two global models, it is clear that
our model is much sharper at few locations. At 100 and 200km, Eifel
hotspot is clearly seen in our models, as well as in EU60. At 400km
and 600km, the subduction is very consistent between GLAD-M25 and EU60,
with the curved shape at the lower bottom of the figure,
while S362ANI+M shows very smooth shape and S40RTS shows much smaller 
perturbation values. Besides, at 400km, GLAD-M25 is enhancing Iceland
compared to S362ANI+M.

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
  \caption{Map views of $V_s$ variations of Europe at various depths for our
  model GLAD-M25(first column) and global(S362ANI+M and S40RTS) and
  regional(EU60\citep{zhu2015seismic}) models. For EU60, the range of color
  bar is 4\% for all depths, which is labeled in the right bottom of the figures.}
\label{fig:europe-vs}
\centering
\end{figure}

@@

Our model at Asian region is plotted on Fig.\ref{fig:asia-vs},
together with S362ANI+M, S40RTS and EARA2014\cite{chen2015multiparameter}.
EARA2014 is a regional 3D anisotropic tomographic model using adjoint
methods, comprising 1.7million frequency-dependent traveltime
measurements from 227 earthquakes recorded by 1869 seismic stations.
It has superior data coverage, mainly by incorporating the China
Seismic Array in this area.

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.pdf}
  \caption{Map views of $V_s$ variations of Asia at various depths for our model GLAD-M25(first column) and several global(S362ANI+M and S40RTS) and regional(EARA2014\citep{chen2015multiparameter}) models.}
\label{fig:asia-vs}
\centering
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
  \caption{Map views of $V_p$ variations of South America at various depths for our model GLAD-M25(first column) and several global models, including S362ANI+M, LLNL-G3Dv3 and GAP-P4\citep{fukao2013subducted}.}
\label{fig:southamerica-vp}
\centering
\end{figure}

@@

@@

This research used resources of the Oak Ridge Leadership Computing Facility, which is a DOE Office of Science User Facility supported under contract DE-AC05-00OR22725.
Additional computational resources were provided by the Princeton Institute for Computational Science \& Engineering (PICSciE).
We acknowledge IRIS ({\tt iris.edu}) and ORFEUS ({\tt orfeus-eu.org}) for providing the data used in this study. We thank Ryan Modrak, Ridvan Orsvuran, Frederik Simons, and James Smith for fruitful discussions.
The open source spectral-element software package SPECFEM3D\_GLOBE and the seismic measurement software package FLEXWIN used for this article are freely available via the Computational Infrastructure for Geodynamics (CIG; {\tt geodynamics.org}). This research was supported by NSF grant~1644826.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
  \caption{Source corrections for 1,040 out of 1,480 events used in the structural inversion. (a) Map view of depth changes. (b) Distribution of seismographic stations used for source inversions. (c) Depth change relative to the original global CMT Catalog depth. (d)--(f) Histograms of depth, origin time, and scalar moment changes relative to the CMT Catalog.
  }
  \label{fig:source_correction}
\end{figure}

@@

The inversion went through ten iterations in a number of stages, as documented in this section.
The evolution of the overall misfit function~(\ref{eq:misfit}) as well as its behavior in the various measurement categories is summarized in Fig.~\ref{fig:misfit}.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/misfit.pdf}
  \caption{Evolution of phase misfits from GLAD-M15 to GLAD-M25.
  Each color denotes the different stages of inversions, between
  which we make changes to the inversion by either tuning the
  weighting strategies or adding more data.
  (a) Evolution of the total phase misfit. (b) - (j) Misfit in
  each period band and component. (e) - (g) From GLAD-M18,
  we future split the 40-100 sec period band into two
  measurement categories: body(red diamond) waves and surface waves
  (red square).
  {\color{red} Wenjie, why do the graphs overlap at iteration 22, but not at iteration 18? Shouldn't 22 look like 18, i.e., no overlapping points?}
  }
  \label{fig:misfit}
\end{figure}

@@

The misfit reduction for 17--40~s body waves (Figs.~\ref{fig:misfit}b--d) tapers off by iteration 21, prompting us to add more earthquakes and change the weighting strategy again by reintroducing the 17--40~s surface waves.

@@

At iteration~22 we added another 440 earthquakes to the database,
bringing the total to 1,480 event,
and we changed the 40--100~s surface wave weights back to their setting in Stage~I.
During this stage we switched from a nonlinear conjugate gradient optimization algorithm to an L-BFGS quasi-Newton method.

\subsection{Misfit assessment}
\label{section:Misfit assessment}

In the previous sections we discussed the evolution of the misfit through three key stages of the inversion.
It is important to note that ``the misfit function'' is, in fact, a continually moving target, because at every iteration the number of measurements increases as the model improves,
and the number of earthquakes increases at iterations~18 and~22.

In this section we calculate specific changes in misfit using all 1,480 earthquakes and an identical set of weightings and windows for three models, namely, GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
Table~\ref{table:misfit_reduction_M15_M25} summarizes the changes in fit in the twelve measurement categories
between the new model, GLAD-M25, and its starting model, GLAD-M15, and between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.
In all categories we observe significant misfit reductions,
with dispersive 40--100~s surface waves exhibiting the largest improvements.
The improvements in fit per component are comparable in all period bands,
indicating that the various categories are reasonably well balanced in the assessment of misfit.

{\color{red} Wenjie: Make sure the variance reductions are calculated as ln (Phi\_M25 / Phi\_M15).}

@@

\subsection{Histogram comparisons}
\label{section:Histogram comparisons}

Another way to evaluate model performance is by assessing the distribution
of measurements in the various categories.
Again we use all 1,480 events and a set of identical windows on all three components
to assess GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
The total number of selected windows exceeds 18~million.
Fig~\ref{fig:phase_hist} shows histograms of the resulting phase
measurements in all twelve measurement categories.
We observe that the distributions generally become better centered on zero,
and that all standard deviations are steadily reduced.
Again we note that the inversion is aimed at reducing the overall misfit,
so there are small tradeoffs between different measurement categories.

Fig~\ref{fig:amp_hist} shows histograms of the amplitude
measurements for all twelve measurement categories,
which were not used in the current inversion.
Despite this,
we observe modest reductions in all standard deviations of the histograms.
The histograms are nicely centered, indicating that the moment magnitudes are suitably selected, because the scalar moment affects all measurement categories equally.
In the next phase of our ongoing inversion we plan to begin assimilating amplitude measurements,
while simultaneously adding shear attenuation as a new model parameter.

@@

\section{Model evaluation}

In this section we evaluate model GLAD-M25 further based on a point-spread function resolution analysis as well as a ``held-out'' dataset, that is, a set of data not used in the actual structural inversion.

\subsection{Point-spread function analysis}

Checkboard tests or tests involving a chosen known structure, e.g., a plume or slab,
are frequently used to evaluate resolution in a tomographic inversion.
Such tests are extremely expensive in FWI and adjoint tomography, because they require roughly the same computational resources as the actual inversion.
In lieu of such tests,
we performed two point-spread function analyses~\citep{fichtner2011resolution,zhu2015seismic,bozdaug2016global}.

\subsection{Held-out dataset}

Following the approach of \cite{tape2009adjoint}, \cite{chen2015multiparameter}, and \cite{bozdaug2016global},
we selected 360 earthquakes that were not used in the actual inversion.
This held-out dataset consists of all magnitude 6.3--7.0 earthquakes in the global CMT catalog that were not used in the inversion.
We chose larger events to generate as many measurements as possible.
We calibrated the centroid time and scalar moment using a grid search based on 3D synthetics calculated in GLAD-M25.
Fig.~\ref{fig:events_360} summarizes the properties of the held-out database.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/events_360.pdf}
  \caption{Summary of the held-out database containing 360 earthquakes. Theses events were not used in the structural inversion. (a) Distribution of events, color coded by depth range as in Fig.~\ref{fig:event_1480}. (b) \& (c) Histograms of moment magnitude and depth.}
  \label{fig:events_360}
\end{figure}

First, we repeated the misfit assessment discussed in Section~\ref{section:Misfit assessment} for the held-out database.
Table~\ref{table:misfit_reduction_M15_M25_360} summarizes the reductions in misfit for the held-out database for model GLAD-M25 compared to GLAD-M15 as well a S362ANI combined with CRUST2.0.
It is comforting to see that the reductions are comparable to the
values tabulated in Table~\ref{table:misfit_reduction_M15_M25} for the actual inversion.
Overall the reductions are slightly smaller, partly due to the fact that we did not conduct full CMT inversions for the held-out database.

@@

Second, we repeated the histogram comparisons discussed in Section~\ref{section:Histogram comparisons} for the held-out database.
We used a set of identical windows on all three components to assess
phase and amplitude anomalies in models GLAD-M25, GLAD-M15, and S362ANI combined with CRUST2.0.
Fig.~\ref{fig:phase_hist_360} shows histograms of the resulting phase
measurements in all twelve measurement categories.
The total number of measurements exceeds 7.8~million.
As in the actual inversion,
we observe systematic decreases in all standard deviations in all twelve categories,
and we note a sharpening of the distributions centered around zero.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dt_histogram_360.pdf}
  \caption{Histogram of phase measurements for the 360 events in the held-out database.}
  \label{fig:phase_hist_360}
\end{figure}

\section{Model GLAD-M25}

In this section we discuss model GLAD-M25 in some detail.
We begin with a global overview of the model before concentrating on specific geographical regions.
We conclude by highlighting various slabs and plumes in the model.

\subsection{Global structure}

We first examine model GLAD-M25 in the context of existing global tomographic models.
In Fig.~\ref{fig:global-vs} we compare global maps of the isotropic part of our shear wavespeed model with model S362ANI$+$M~\citep{moulik2014anisotropic},
which is an updated version of the starting model for the GLAD-M15 inversion,
and model S40RTS~\citep{ritsema2011s40rts}.
The range of perturbations in shear wavespeed varies from map to map, as indicated in the top left of each panel.
Overall these models are in good agreement at the longest wavelengths, especially Glad-M25 and S362ANI$+$M.
The perturbations in GLAD-M15 tend to be larger than in the other models,
consistent with observations by~\cite{french2014whole},
whose model is also based on a form of waveform inversion.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vs.pdf}
  \caption{Map views of global shear wavespeed perturbations at various depths for  model
  GLAD-M25~(left column), S362ANI$+$M~\citep[middle column;][]{moulik2014anisotropic}
  and S40RTS~\citep[right column;][]{ritsema2011s40rts}.
  At a given radius,
  perturbations are calculated relative to each model's average.
  The range of perturbations in shear wavespeed varies from map to map, as indicated in the top left of each panel.
  The green circles denote locations of various
  hotspots~\citep{montelli2006catalogue}.
  The range of the colorbar is the same for each row,
  and its maximum value is indicated in parentheses on the left, after
  the depth.}
  \label{fig:global-vs}
\end{figure}

%\begin{figure}
%\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_S362ANI-LLNL.pdf}
%  \caption{Map views of global $V_p$ variations at various depths for our model GLAD-M25(left column), S362ANI$+$M(middle column) and LLNL-G3Dv3(right column)\citep{simmons2012llnl}. For LLNL-G3Dv3, the depths is labeled on the right bottom based on its own mesh spacing. Other plotting conventions are used similar as in Figure \ref{fig:global-vs}.}
%\label{fig:global-vp}
%\centering
%\end{figure

An important aspect of our inversion is that constrain shear and compressional waves simultaneously.
In Fig.~\ref{fig:global-vs} we compare global maps of our compressional wavespeed model with P models LLNL-G3Dv3~\citep{simmons2012llnl} and GAP-P4~\citep{fukao2013subducted}.
At a depth of 100~km,
GLAD-M25 shows prominent mid-oceanic ridges, cooling of the Pacific lithosphere, and the roots of numerous continental cratons.
In the upper mantle, LLNL-G3Dv3 exhibits the largest lateral variations,
e.g., very slow compressional wavespeeds at 500~km depth below Hawaii, Samoa, and Tahiti.
In the midmantle we can see remnants of subduction beneath South America, Indonesia,
and Tonga-Kermadec.
In the deep mantle, LLNL-G3Dv3 and GAP-P4 begin to fade out, but the long-wavelength patterns,
in particular the lowerparts of the Africa and Pacific superplumes, are very similar.

{\color{red} Wenjie: Note: add spherical harmonic analysis later.}

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/globe_vp_LLNL-GAP.pdf}
  \caption{Map views of global compressional wavespeed variations at various depths for model
  GLAD-M25 (left column), LLNL-G3Dv3 \citep[middle column;][]{simmons2012llnl} and
  GAP-P4~[right column;][](\citep{fukao2013subducted}).
  For LLNL-G3Dv3, depth ranges are labeled on the bottom right
  bottom of each panel. Other plotting conventions are as in Fig.~\ref{fig:global-vs}.}
\label{fig:global-vp}
\centering
\end{figure}

@@

The deployment of USArray has dramatically increased data overage underneath the
continental United States.
In this section, we compare GLAD-M25 with
with two global models, S362ANI$+$M and S40RTS, and two regional models,
US22~\citep{zhu2017radial} and SL2013NA~\citep{schaeffer2014imaging}.
US22 is a radially anisotropic model based on adjoint tomography using
USArray data from 180 regional earthquakes using 15--50~s
body waves and 25--150~s surface waves.
SL2013NA is a global upper-mantle shear wavespeed model based on multimode
surface waveform tomography primarily focused on North America.

North America is characterized by a large, high-wavespeed cratonic
lithosphere, bounded by the Rocky Mountain Front to the West and continental
margin to the East. On both sides the lithosphere has been deformed by
low wavespeed structures, thus forming sharp boundaries.

At 100km, our model shows a much sharpened boundary between the carton
and surrounding low velocity structures, especially compared with
two global models, S362ANI$+$M and S40RTS, yet stay very similar to
two regional models, US22 and SL2014NA. At such depth,
we are observed a very strong expression of the Snake River Plain(
with Yellowstone) and Raton hotspot, with their depth extending to 200km.
The very high-velocity craton extend to 200km, with its very core part to
300 km, similar to US22 while SL2013NA shows it almost disappeared at such depth.
Again, the Wyoming craton and Medicine Hat Block shows a very strong lithosphere
root from the very shallow depth to 400km, which is also similar to US22 but
hard to observe in SL2013NA. Similar case is the craton at Yavapai and
Mazatzal Blocks, which define the southern bound of the large craton.

@@

At the North, our models shows a extended high velocity craton beneath the 
Greenland, though clearly separated with the North America Craton,
bounded at the relatively low velocity structure at Barffin Bay and Labrador
Sea, with North American Craton followed nicely with the coastline. In the
north west region, our models shows the most clear picture of
Aleutian subduction zones, with it high velocity feature down to 400km.
In the northeastern part, the Iceland hotspot has been greatly enhanced,
especially at 300km and 400km compared to S362ANI$+$M.

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/depth_slice/america_vs.pdf}
  \caption{Map views of $V_s$ variations of North America at various depths
  for our model GLAD-M25(first column) and several global(S362ANI$+$M and S40RTS)
  and regional(US22\citep{zhu2017radial} and SL2013NA\citep{schaeffer2014imaging})
  models. Green circles denotes the locations of hotspots. For SL2013NA, we
  showed the 610km instead of 600km due to its own mesh.}
\label{fig:america-vs}

@@

Fig.\ref{fig:europe-vs} shows the isotropic $V_s$ structures at Europe. As
comparisons, we also showed S362ANI$+$M, S40RTS and one regional model EU60
\citep{zhu2015seismic}. Compared to two global models, it is clear that
our model is much sharper at few locations. At 100 and 200km, Eifel
hotspot is clearly seen in our models, as well as in EU60. At 400km
and 600km, the subduction is very consistent between GLAD-M25 and EU60,
with the curved shape at the lower bottom of the figure,
while S362ANI$+$M shows very smooth shape and S40RTS shows much smaller 
perturbation values. Besides, at 400km, GLAD-M25 is enhancing Iceland
compared to S362ANI$+$M.

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/europe_vs.pdf}
  \caption{Map views of $V_s$ variations of Europe at various depths for our
  model GLAD-M25(first column) and global(S362ANI$+$M and S40RTS) and
  regional(EU60\citep{zhu2015seismic}) models. For EU60, the range of color
  bar is 4\% for all depths, which is labeled in the right bottom of the figures.}
\label{fig:europe-vs}
\centering
\end{figure}

@@

Our model at Asian region is plotted on Fig.\ref{fig:asia-vs},
together with S362ANI$+$M, S40RTS and EARA2014\cite{chen2015multiparameter}.
EARA2014 is a regional 3D anisotropic tomographic model using adjoint
methods, comprising 1.7million frequency-dependent traveltime
measurements from 227 earthquakes recorded by 1869 seismic stations.
It has superior data coverage, mainly by incorporating the China
Seismic Array in this area.

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/asia_vs.pdf}
  \caption{Map views of $V_s$ variations of Asia at various depths for our model GLAD-M25(first column) and several global(S362ANI$+$M and S40RTS) and regional(EARA2014\citep{chen2015multiparameter}) models.}
\label{fig:asia-vs}
\centering
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.9\textwidth]{figures/depth_slice/south_america_vp.pdf}
  \caption{Map views of $V_p$ variations of South America at various depths for our model GLAD-M25(first column) and several global models, including S362ANI$+$M, LLNL-G3Dv3 and GAP-P4\citep{fukao2013subducted}.}
\label{fig:southamerica-vp}
\centering
\end{figure}

@@

In summary,
the new model performs well for the held-out dataset, both in terms of misfit reductions and measurement distributions in all twelve measurement categories.
We expect to see similar behavior for any future earthquakes.

@@

This research used resources of the Oak Ridge Leadership Computing Facility, which is a DOE Office of Science User Facility supported under contract DE-AC05-00OR22725.
Additional computational resources were provided by the Princeton Institute for Computational Science \& Engineering (PICSciE).
We acknowledge IRIS ({\tt iris.edu}) and ORFEUS ({\tt orfeus-eu.org}) for providing the data used in this study.
{\color{red} Wenjie: Please add all relevant data centers.} We thank Ryan Modrak, Ridvan Orsvuran, Frederik Simons, and James Smith for fruitful discussions.
The open source spectral-element software package SPECFEM3D\_GLOBE and the seismic measurement software package FLEXWIN used for this article are freely available via the Computational Infrastructure for Geodynamics (CIG; {\tt geodynamics.org}). This research was supported by NSF grant~1644826.
